Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-09-11 review_article.Rmd
Interactivity section restored

Cancer maps are effective tools for communicating to wide range of audiences, including the general public and others not trained in statistical analyses. These visualisation enable thse non-expert audiences to access the outputs of sophisticated statistical analyses. Cruickshank's (1947) as cited by @DMAHP, discusses using visuals as a 'formal statistical assessment of the spatial pattern'. Overwhelmingly cancer maps utilised to communicate to the public and other non-expert audiences are choropleths.

## Overview

@roberts2019communication identified 33 publicly available cancer atlases, published between January 2010 and November 2015. All of these use choropleth maps. All but one of these were published by non-commercial organisations, including not-for-profits, government, research organisations, advocacy groups or government funded partnerships. The use of choropleths within the public domain mirrors the heavy use of choropleth maps within the research literature, discussed above. 
The cancer atlases covered geographies from all around the world, most focused on single nations. Figure \@ref(choropleth-grid-create) displays a global (b), national (a,d,e,f) and state (c,g) choropleths.

>>>>

Cancer maps are effective tools for communicating to wide range of audiences, including the general public and others not trained in statistical analyses. These visualisation enable thse non-expert audiences to access the outputs of sophisticated statistical analyses. Cruickshank's (1947) as cited by @DMAHP, discusses using visuals as a 'formal statistical assessment of the spatial pattern'. Overwhelmingly cancer maps utilised to communicate to the public and other non-expert audiences are choropleths. A grey literature review of cancer atlases available in the public domain [@roberts2019communication] identified 33 cancer atlases published on the internet between January 2010 and November 2015, all of which were choropleths. These maps were published by non-commercial organisations, including not-for-profits, government, research organisations, advocacy groups or government funded partnerships.Only one map was published by a commercial entity.  The use of choropleths within the public domain mirrors the heavy use of choropleth maps within the research literature, discussed above. 
The cancer atlases covered geographies from all around the world, most focused on single nations.
Figure \@ref(choropleth-grid-create) displays a global (b), national (a,d,e,f) and state (c,g) choropleths.
